Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-20 3dpas_intro.tex
locally versus geographically distributed
remove reference to detailed streaming discussion that does not exist

There are many ways to address distributed data.  These include but
are not limited to:
% Ways to manage \katznote{?} the
% distribution include but are not limited to:
\begin{itemize}
\item \textbf{Replication:} Data is duplicated on multiple nodes. When
  fully replicated, each execution unit has access to the same
  data. Replication can be partial, i.e., data can be replicated to a
  subset of resources. The degree of replication quantifies the
  average of the number of copies of each data item. Replication may
  be non-uniform, e.g., if only a subset of data (perhaps ``hot''
  data) is replicated. Caching is a lightweight form of replication.
\item \textbf{Partitioning:} Data is divided and distributed across
  multiple nodes. Different forms of partitioning exist.  For example,
  data can be thematically partitioned with respect to its type, such
  as sensor data vs. simulated data, or data can be partitioned
  according to a spatial or temporal attributes. This can be an opaque
  (e.g., ID) and or a domain dependent (e.g., spatial) attribute.
\item \textbf{Streaming}: A form of distributed data processing in
  which data arrives from a source; often the stream is a steady,
  continuous flow, but often it fluctuates both spatially and
  temporally. Also, typically, the stream of data must be processed in
  near real-time. Streaming thus also has attributes of dynamism, which is
  discussed in the next subsection.
\end{itemize}

@@

\item Details of the storage system are often not known. Often data is
  stored in a distributed way, e.g., on a distributed file system,
  which commonly fits into the medium degree of distribution (the same
  data center).

>>>>

There are many ways to address distributed data.  These include but
are not limited to:
% Ways to manage \katznote{?} the
% distribution include but are not limited to:
\begin{itemize}
\item \textbf{Replication:} Data is duplicated on multiple nodes. When
  fully replicated, each execution unit has access to the same
  data. Replication can be partial, i.e., data can be replicated to a
  subset of resources. The degree of replication quantifies the
  average of the number of copies of each data item. Replication may
  be non-uniform, e.g., if only a subset of data (perhaps ``hot''
  data) is replicated. Caching is a lightweight form of replication.
\item \textbf{Partitioning:} Data is divided and distributed across
  multiple nodes. Different forms of partitioning exist.  For example,
  data can be thematically partitioned with respect to its type, such
  as sensor data vs. simulated data, or data can be partitioned
  according to a spatial or temporal attributes. This can be an opaque
  (e.g., ID) and/or a domain dependent (e.g., spatial) attribute.
\item \textbf{Streaming}: A form of distributed data processing in
  which data arrives from a source; often the stream is a steady,
  continuous flow, but often it fluctuates both spatially and
  temporally. Also, typically, the stream of data must be processed in
  near real-time. 
  %Streaming thus also has attributes of dynamism, which is
  %discussed in the next subsection.
\end{itemize}

@@

\item Details of the storage system are often not known. Often, data is
  stored in a distributed way, e.g., on a distributed file system in the same
  data center (locally distributed).
